### 2018-04-19 Paper/jaccardbaetica.tex
add new changes material

The chronology in the workshops is widely diverse from the first to the third centuries AD (CITAR). Some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. A reason may be that most of them were partially excavated and only focused on archaeological surveys to collect the maximum stamps as possible (CITAR)

@@

From the database, we collected the following information: a) the site where it was found and b) the stamp code. We also created a new column with the area where stamps were found. Those areas, known as \textit{conventus}, were administrative centers for territorial organization in the Roman Empire (CITAR). Dressel 20 stamps were found in three different \textit{conventus}: Hispalis (currently Seville), Corduba (currently C\'ordoba) and Astigi (currently Écija, Sevilla) \citep{rodriguez_economioleicola_1977,chic_datos_2001,berni_millet_epigrafianforica_2008} .
AQUÍ QUIZÁS HABLAR DE SELLOS NO?

@@

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/dendro}
\caption{Dendrogram obtained by Morisita-Horn algorithm of different amphora workshops in Baetica area. Colors are represented by areas}
\label{dendro}
\end{figure}

>>>>

The chronology in the workshops is widely diverse from the first to the third centuries AD (CITAR). Some stamps show a more specific chronology while the majority of them display a large activity of production being difficult to specify an accurate chronology. This could be due to two reasons. First, most of workshops were partially excavated and focused on archaeological surveys in order to collect the maximum stamps as possible. They presented a long chronology. Second, this amphora type was produced during almost three centuries with apparently few changes (PODRÍA CITARME AQUÍ MUAHA)

@@

From the database, we collected the following information: a) the site where it was found and b) the stamp code. We also created a new column with the area where stamps were found (decir berni). Those areas, known as \textit{conventus}, were administrative centers for territorial organization in the Roman Empire (CITAR). Dressel 20 stamps were found in three different \textit{conventus}: Hispalis (currently Seville), Corduba (currently C\'ordoba) and Astigi (currently Écija, Sevilla) \citep{rodriguez_economioleicola_1977,chic_datos_2001,berni_millet_epigrafianforica_2008} .

The distribution of amphora stamps in different conventus can be seen in Fig. 2. The majority of stamps found are concentrated in Hispalis with ... stamps while Astigi and Corduba concentrated  respectivamently. Mostly workshops show a homogeneity of distribution except La Catria or bla bla that show a big amount of stamps.  
%explicar por qué: mayor intensifación en las excavaciones

explicar las razones del conventus no?
AQUÍ QUIZÁS HABLAR DE SELLOS NO?

@@

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/dendro}
\caption{Dendrogram obtained by Morisita-Horn algorithm of different amphora workshops in Baetica area. Colors are represented by areas divided into Hispalis (red), Astigi (green) and Corduba (blue)}
\label{dendro}
\end{figure}
